%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Product Manager} % Organisation
    {Pixxel } % Project
    {Bengaluru} % Location
    {August 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        % \item {\textbf{MVP Definition: }Headed 20 alpha customer feedback assimilation \& market research post alpha release, assisting in roadmap curation for beta launch.}
        %  \item {\textbf{Machine Learning Models: }Orchestrated the entire user journey architecture of 5 ML models by brainstorming with geospatial analysts \& alpha users.}
        % \item {\textbf{Product ownership: }Conceptualized the highest revenue product line; Satellite tasking dashboard, API ordering, and administration portal, orchestrating the integration of work from diverse teams within a tight time frame of 20 days.}
        % \item {\textbf{Competitive Research \& GTM: }Supported competitor benchmarking \& go-to-market activities, including research of over 100 industry leaders, the trends \& solutions. Created marketing collateral,  product demos, \& investor decks.}
        % \item {\textbf{Product Guide: }Designed a user guide that reduced onboarding time by 25\%, and gathered feedback from first 20 customers post-launch to refine the product roadmap and prioritization}
        \item {\textbf{AI/ML Models: }Onboarded \& orchestrated the entire user journey architecture of 10+ models on the platform, working with data scientists \& clients.}
        \item {\textbf{Product Ownership: }Designed the highest-revenue product line, including a satellite tasking dashboard \& API ordering, in <30 days. Led product lifecycle of the IAM, designing granular user permissions critical for enterprise onboarding and scalability.}
        \item {\textbf{Analytics and Compliance: }Architected dashboards with Metabase \& Grafana; ensured compliance by leading EULA and privacy policy implementation.}
        \item {\textbf{Product Guide: }Designed user guide, cutting onboarding time by 25\% \& gathered feedback from first 20 customers for roadmapping \& prioritization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Product Management Intern} % Organisation
    {LambdaTest } % Project
    {Noida (Hybrid)} % Location
    {June 2022 ‑ Jan 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {\textbf{PRD Creation:  }Authored \& executed 6 comprehensive PRDs for new feature releases, outlining user flows \& deploying Figma for intuitive designs.}
        \item {\textbf{Cross-Platform App:  }Led development of cross-platform Android \& iOS app from scratch, enabling over 200 clients to test product offerings.}
        \item {\textbf{Document Repository:  }Created \& maintained a 50 document repository on Github \& product website, including feature demos \& sample scripts.}
        \item {\textbf{Analytical Frameworks:  }Used a suite of analytical frameworks including Happy Path Funnels, Cohort Analysis, Event Tracking, A/B Testing, \& User Segmentation to bolster product engagement by an impactful 5\%.}
        % \item {Supported the product launch and go-to-market activities, including creating marketing collateral, conducting product demos, and providing help to the sales and customer success teams.}
      \end{cvitems}
    }

% ---------------------------------------------------------
  \cventry
    {Growth Product Intern} % Organisation
    {Languify} % Project
    {Remote} % Location
    {June 2021 ‑ July 2021} % Date(s)
    % {Languify (AI) is a global B2B SaaS ecosystem that monitors and helps your improve communication skills. My role included the following:} % Description
    {
      \begin{cvitems} % Description(s) of project
        \item {\textbf{Waitlist Program:  }Devised growth \& social media strategy for waitlist program, boosting acquisition \& engagement, increasing conversion rate by 10\%.}
        \item {\textbf{Analytics:  }Optimized performance using Google Analytics reducing bounce rate by 8\% \& integrating data driven approach to marketing.}
        \item {\textbf{Campus Ambassador Program:  }Reached 10,000+ students through targeted campaigns, boosting brand awareness by 20\%.}
        \item {\textbf{Zoho Campaigns:  }Integrated Zoho automation to enhance email \& social media campaigns, leading to a 15\% boost in email CTR \& 50\% follower growth.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Business Development Intern} % Organisation
    {Niroggyan} % Project
    {Remote} % Location
    {April 2020 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {\textbf{Client onboarding:  }Refined client integration processes with external providers to overcome operational challenges, surging MAU by 10\%.}
        \item {\textbf{Market Analysis:  }Conducted market analysis and competitor research to enhance sales strategies and optimize customer acquisition efforts.}
        \item {\textbf{Sales:  }Collaborated with the business development team to initiate and negotiate partnerships, driving market presence and revenue growth.}
        % \item {\textbf{Technical Skills:} Tableau, Overleaf, LaTeX.}
        % \item {\textbf{Soft Skills:} Time Management, Teamwork, Presentation skills, Report writing.}
      \end{cvitems}
    }



\end{cventries}
